How reliable are inferences from state-space age-structured assessment models?

### 2023-01-06 Project_0/paper/paper.tex
more SR AIC analysis

  pdftitle={State-space age-structured assessment models provide reliable inferences(?)},

@@

\title{State-space age-structured assessment models provide reliable
inferences(?)}
\author{Timothy J. Miller\textsuperscript{1}, Britten, Brooks, Fay,
Legault, Stock,}
\date{}

@@

>>>>

  pdftitle={How reliable are inferences from state-space age-structured assessment models?},

@@

\title{How reliable are inferences from state-space age-structured
assessment models?}
\author{Timothy J. Miller\textsuperscript{1}, Britten, Brooks, Fay,
Legault, Stock,}
\date{}

@@

\begin{figure}
\caption{Predicted probability of AIC being better for BH model.}\label{glm_res_NAA_re}
\begin{center}
\includegraphics[width = \textwidth]{pred_SR_best_NAA_oms.png}
\end{center}
\end{figure}

\hypertarget{m-operating-models}{%
\subsection{M operating models}\label{m-operating-models}}

\hypertarget{estimating-models-include-naa-random-effects-and-estimation-assumes-mean-r-or-bh-sr-1}{%
\subsubsection{Estimating models include NAA random effects and
estimation assumes mean R or BH
SR}\label{estimating-models-include-naa-random-effects-and-estimation-assumes-mean-r-or-bh-sr-1}}

\begin{table}
\caption{M random effects operating models.}
{\input{M_om_em_R_BH_aic_table}}
\end{table}
\clearpage
